Assessing primitives performance\\ on multi-stage execution

### 2018-05-02 paper.tex
started implem ctxt

%% Title information
\title[Short Title]{Assessing primitives performance\\ on multi-stage execution}

@@

Our evaluation is based on the Cog

\subsection{VM execution.}

\cite{blueBook}
\cite{PharoByExample,SqueakByExample, NewspeakOopsla}
\cite{BackToTheFuture, CogJIT}
exec hybrid interp JIT.

Impl langage.

Il faut expliquer le process de compilation de la VM. (Slang -> C, C-> ASM, au runtime JIT ST->ASM)
 execution with C and St stack

@@

@@

\subsection{Primitive execution.}

@@

\subsection{String comparison primitive.}
\label{subsec:primSpec}

>>>>

%% Title information
\title[Assessing primitives performance on multi-stage execution]{Assessing primitives performance\\ on multi-stage execution}

@@

Our evaluation is based on the Cog VM a Smalltalk virtual machine. The Cog VM is based on Dan Ingalls' Smalltalk VM \cite{BackToTheFuture} and have been enhanced with a JIT \cite{CogJIT} compiling one method or closure at a time to native code. Historically, the VM implemented a 32-bits adaptation of the Smalltalk-80 specifications \cite{blueBook}, but the Cog VM is now the default VM for multiple programming languages such as Pharo \cite{PharoByExample}, Squeak \cite{SqueakByExample} and Newspeak \cite{NewspeakOopsla}.

Section \ref{sec:VMCompil} describes briefly the implementation languages and compilation process of the Cog VM. Section \ref{sec:VMexec} explains briefly the hybrid execution model with an interpreter and a JIT. In Section \ref{sec:primExec}, we detail how primitives are executed. Section \ref{subsec:primSpec} discusses the specifications of the string comparison primitive used for our evaluation.

\subsection{VM compilation}
\label{sec:VMCompil}

Similar to \cite{RPythonToolchain}

Impl langage. JIT.

Il faut expliquer le process de compilation de la VM. (Slang -> C, C-> ASM,

@@

\subsection{VM execution}
\label{sec:VMexec}

exec hybrid interp 
 au runtime JIT ST->ASM)
 execution with C and St stack

@@

\subsection{Primitive execution}
\label{sec:primExec}

@@

\subsection{String comparison primitive}
\label{subsec:primSpec}
